Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
more random errors

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\bullet}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.  SN Ia heating depends also on a convolution of the DTD (eq. [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.  We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.  Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.

>>>>

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for black holes of mass $\Mbh = 10^{6} \Msun$ (top panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The heating and mass input parameters due to stellar winds, $v_{w}^{\star}(\tau_{\star})$ and $\eta(\tau_{\star})$, are calculated as described in Appendix~\ref{app:windheat} (Fig.~\ref{fig:vwImp}).  The heating from SN Ia ($v_{w}^{\rm Ia}$) and Compton heating ($v_{\rm w}^{\rm C}$) are calculated from equations~\eqref{eq:vIa} and~\eqref{eq:vC} respectively, also making use of $\eta(\tau_{\star})$ from stellar winds.  SN Ia heating depends also on a convolution of the DTD (eq. [\ref{eq:DTD}]) and the star formation history, which reduces to the DTD itself for a single star burst.  We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by attenuating $v_{w}^{\rm Ia}$ by a factor $e^{-\rs/\rIa}$, where $r_{\rm Ia}$ is the radius exterior to which the time between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.  Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not plotted for clarity.
